---
title: "Untitled"
author: "LYH"
date: "3/30/2022"
output: html_document
---


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r}


safe_divide <- function(a, b) {
  return (ifelse(b == 0, 0, a/b))
}


# takes in a number and number of decimal places to round to, returns a percentage string
# e.g. to_pctg(0.75229, 2) returns "75.23%"
to_pctg <- function(x, dp) {
  val_pctg = round(x * 100, dp)
  return (paste0(val_pctg, "%"))
}


```



```{r}

# v is a character vector containing column names to remove
delete_cols <- function(df, v) {
  return (df[, !(names(df) %in% v)])
}

# v is a character vector containing column names to get unique values of
get_unique_cols <- function(df, v) {
  return (unique(df[v]))
}

get_race <- function(num) {
  races_vector <- c("Black/African American", "European/Causasian-American", "Latino/Hispanic American", "Asian/Pacific Islander/Asian-American", "Native American", "Other")
  if (is.na(num)) {
    return (NA);
  } else {
    return (races_vector[num])
  }
}
get_race_vec <- Vectorize(get_race)

get_field_cd <- function(num) {
  fields_vector <- c("Law", "Math", "Social Science, Psychologist", "Medical Science, Pharmaceuticals, and Bio Tech", "Engineering", "English/Creative Writing/ Journalism", "History/Religion/Philosophy", "Business/Econ/Finance", "Education, Academia", "Biological Sciences/Chemistry/Physics", "Social Work", "Undergrad/undecided", "Political Science/International Affairs", "Film", "Fine Arts/Arts Administration", "Languages", "Architecture", "Other")
  if (is.na(num)) {
    return (NA);
  } else {
    return (fields_vector[num])
  }
}
get_field_cd_vec <- Vectorize(get_field_cd)

get_goal <- function(num) {
  v <- c("Seemed like a fun night out", "To meet new people", "To get a date", "Looking for a serious relationship", "To say I did it", "Other")
  if (is.na(num)) {
    return (NA);
  } else {
    return (v[num])
  }
}
get_goal_vec <- Vectorize(get_goal)

get_date_freq <- function(num) {
  v <- c("Several times a week", "Twice a week", "Once a week", "Twice a month", "Once a month", "Several times a year", "Almost never")
  if (is.na(num)) {
    return (NA);
  } else {
    return (v[num])
  }
}
get_date_freq_vec <- Vectorize(get_date_freq)

get_go_out_freq <- function(num) {
  v <- c("Several times a week", "Twice a week", "Once a week", "Twice a month", "Once a month", "Several times a year", "Almost never")
  if (is.na(num)) {
    return (NA);
  } else {
    return (v[num])
  }
}
get_go_out_freq_vec <- Vectorize(get_go_out_freq)

get_career_category <- function(num) {
  v <- c("Lawyer", "Academic/Research", "Psychologist", "Doctor/Medicine", "Engineer", "Creative Arts/Entertainment", "Banking/Consulting/Finance/Marketing/Business/CEO/Entrepreneur/Admin", "Real Estate", "International/Humanitarian Affairs", "Undecided", "Social Work", "Speech Pathology", "Politics", "Pro sports/Atheletics", "Other", "Journalism", "Architecture")
  if (is.na(num)) {
    return (NA);
  } else {
    return (v[num])
  }
}
get_career_category_vec <- Vectorize(get_career_category)



# 0-3 -> Low preference
# 4-7 -> Mid preference
# 8-10 -> High preference
pref_to_category <- function(num) {
  if (num <= 3) {
    return ("Low")
  } else if (num <= 7) {
    return ("Mid")
  } else {
    return ("High")
  }
}
pref_to_category_vec <- Vectorize(pref_to_category)



```


Data was gathered from participants in experimental speed dating events from 2002-2004. During the events, the attendees would have a four minute "first date" with every other participant of the opposite sex. At the end of their four minutes, participants were asked if they would like to see their date again. They were also asked to rate their date on six attributes: Attractiveness, Sincerity, Intelligence, Fun, Ambition, and Shared Interests.

The dataset also includes questionnaire data gathered from participants at different points in the process. These fields include: demographics, dating habits, self-perception across key attributes, beliefs on what others find valuable in a mate, and lifestyle information. See the Speed Dating Data Key document below for details.

```{r}
# https://www.kaggle.com/datasets/annavictoria/speed-dating-experiment?resource=download
data <- read.csv("Speed Dating Data.csv")

# save a copy
original_data <- data
```

```{r}

# rename columns
data <- data %>% rename(
  partner_id = pid,
  is_male = gender,
  interests_correlation_at_signup = int_corr,
  partner_age = age_o,
  partner_race = race_o,
  partner_preference_for_attractiveness = pf_o_att,
  partner_preference_for_sincerity = pf_o_sin,
  partner_preference_for_intelligence = pf_o_int,
  partner_preference_for_fun = pf_o_fun,
  partner_preference_for_ambition = pf_o_amb,
  partner_preference_for_shared_interests = pf_o_sha,
  event_night_decision_by_partner = dec_o,
  event_night_rating_by_partner_on_attractiveness = attr_o,
  event_night_rating_by_partner_on_sincerity = sinc_o,
  event_night_rating_by_partner_on_intelligence = intel_o,
  event_night_rating_by_partner_on_fun = fun_o,
  event_night_rating_by_partner_on_ambition = amb_o,
  event_night_rating_by_partner_on_shared_interests = shar_o,
  how_much_does_partner_like_you = like_o,
  probability_partner_says_yes_to_you = prob_o,
  partner_has_met_you_before = met_o
)

# clean columns
data$is_male = as.logical(data$is_male)
data$match = as.logical(data$match)
data$samerace = as.logical(data$samerace)
data$partner_has_met_you_before = data$partner_has_met_you_before == 1
data$event_night_decision_by_partner = as.logical(data$event_night_decision_by_partner)
data$partner_race = get_race(data$partner_race)

# delete irrelevant columns
cols_to_remove <- c("id", "idg", "condtn", "round", "position", "positin1", "order", "partner")
data <- delete_cols(data, cols_to_remove)

```



# Info on each participant

```{r}

# remove columns that are unique to the individual participant, put it in a new dataframe

unique_characteristics <- c("age", "field", "field_cd", "undergra", "mn_sat", "tuition", "race", "imprace", "imprelig", "from", "zipcode", "income", "goal", "date", "go_out", "career", "career_c", "sports", "tvsports", "exercise", "dining", "museums", "art", "hiking", "gaming", "clubbing", "reading", "tv", "theater", "movies", "concerts", "music", "shopping", "yoga", "exphappy", "expnum")

distinct_participants_cols <- c(c("iid", "is_male"), unique_characteristics)

participants_data <- get_unique_cols(data, distinct_participants_cols) %>% rename(
  field_of_study = field,
  field_of_study_category = field_cd,
  undergrad_sch = undergra,
  median_SAT_of_undergrad_sch = mn_sat,
  tuition_of_undergrad_sch = tuition,
  importance_of_race = imprace,
  importance_of_religion = imprelig,
  median_income_of_zipcode = zipcode,
  goal_of_participating = goal,
  freq_of_going_on_dates = date,
  freq_of_going_out = go_out,
  intended_career = career,
  intended_career_category = career_c,
  expectation_of_happiness_of_matches = exphappy,
  expected_num_of_people_interested_in_me_out_of_twenty = expnum
) %>% mutate(
  field_of_study_category = get_field_cd_vec(field_of_study_category),
  race = get_race_vec(race),
  goal_of_participating = get_goal_vec(goal_of_participating),
  freq_of_going_on_dates = get_date_freq_vec(freq_of_going_on_dates),
  freq_of_going_out = get_go_out_freq_vec(freq_of_going_out),
  intended_career_category = get_career_category_vec(intended_career_category)
)

data <- delete_cols(data, unique_characteristics)

file_name = paste0("participants_data", ".csv")
write.csv(participants_data, file_name, row.names = FALSE)

```


## At sign up

### What do you look for in the opposite sex?

Waves 6-9: Please rate the importance of the following attributes in a potential date on a scale of 1-10 (1=not at all important, 10=extremely important)

Waves 1-5, 10-21: You have 100 points to distribute among the following attributes -- give more points to those attributes that are more important in a potential date, and fewer points to those attributes that are less important in a potential date.  Total points must equal 100.

Attractiveness + Sincerity + Intelligence + Fun + Ambitions + Shared Interests = 100

```{r}

look_for_in_opp_sex_at_signup_cols <- c("attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1", "shar1_1")

distinct_cols <- c(c("iid", "wave", "is_male"), look_for_in_opp_sex_at_signup_cols)

look_for_in_opp_sex_at_signup <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr1_1,
  sincerity = sinc1_1,
  intelligence = intel1_1,
  fun = fun1_1,
  ambition = amb1_1,
  shared_interests = shar1_1,
)

data <- delete_cols(data, look_for_in_opp_sex_at_signup_cols)

file_name = paste0("look_for_in_opp_sex_at_signup", ".csv")
write.csv(look_for_in_opp_sex_at_signup, file_name, row.names = FALSE)

```

### What do you think others (of your gender) look for in the opposite sex?

Waves 6-9: Please rate the importance of the following attributes on a scale of 1-10 (1=not at all important, 10=extremely important):

Waves 10-21 : You have 100 points to distribute among the following attributes -- give more points to those attributes that you think your fellow men/women find more important in a potential date and fewer points to those attributes that they find less important in a potential date.  Total points must equal 100.

Attractiveness + Sincerity + Intelligence + Fun + Ambitions + Shared Interests = 100

```{r}

others_look_for_in_opp_sex_at_signup_cols <- c("attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1", "shar4_1")

distinct_cols <- c(c("iid", "wave", "is_male"), others_look_for_in_opp_sex_at_signup_cols)

others_look_for_in_opp_sex_at_signup <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr4_1,
  sincerity = sinc4_1,
  intelligence = intel4_1,
  fun = fun4_1,
  ambition = amb4_1,
  shared_interests = shar4_1,
)

data <- delete_cols(data, others_look_for_in_opp_sex_at_signup_cols)

file_name = paste0("others_look_for_in_opp_sex_at_signup", ".csv")
write.csv(others_look_for_in_opp_sex_at_signup, file_name, row.names = FALSE)

```


### What do you think the opposite sex looks for in a date?

Waves 6-9: Please rate the importance of the following attributes on a scale of 1-10 (1=not at all important, 10=extremely important):

Waves 1-5 and 10-21: Please distribute 100 points among the following attributes -- give more points to those attributes that you think are more important to members of the opposite sex when they are deciding whether to date someone.  Total points must equal 100.

Attractiveness + Sincerity + Intelligence + Fun + Ambitions + Shared Interests = 100

```{r}

opp_sex_looks_for_in_date_at_signup_cols <- c("attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1", "shar2_1")

distinct_cols <- c(c("iid", "wave", "is_male"), opp_sex_looks_for_in_date_at_signup_cols)

opp_sex_looks_for_in_date_at_signup <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr2_1,
  sincerity = sinc2_1,
  intelligence = intel2_1,
  fun = fun2_1,
  ambition = amb2_1,
  shared_interests = shar2_1,
)

data <- delete_cols(data, opp_sex_looks_for_in_date_at_signup_cols)

file_name = paste0("opp_sex_looks_for_in_date_at_signup", ".csv")
write.csv(opp_sex_looks_for_in_date_at_signup, file_name, row.names = FALSE)

```


### Opinion of own attributes?

Please rate your opinion of your own attributes, on a scale of 1-10 (be honest!):

Attractiveness, Sincerity, Intelligence, Fun, Ambitions, Shared Interests

```{r}

self_perception_at_signup_cols <- c("attr3_1", "sinc3_1", "intel3_1", "fun3_1", "amb3_1")

distinct_cols <- c(c("iid", "is_male"), self_perception_at_signup_cols)

self_perception_at_signup <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr3_1,
  sincerity = sinc3_1,
  intelligence = intel3_1,
  fun = fun3_1,
  ambition = amb3_1,
)

data <- delete_cols(data, self_perception_at_signup_cols)

file_name = paste0("self_perception_at_signup", ".csv")
write.csv(self_perception_at_signup, file_name, row.names = FALSE)

```


### How do you think others perceive you?

Please rate yourself how you think others would rate you on each of the following attributes, on a scale of 1-10 (1=awful, 10=great):

Attractiveness, Sincerity, Intelligence, Fun, Ambitions, Shared Interests

```{r}

others_perception_of_self_at_signup_cols <- c("attr5_1", "sinc5_1", "intel5_1", "fun5_1", "amb5_1")

distinct_cols <- c(c("iid", "is_male"), others_perception_of_self_at_signup_cols)

others_perception_of_self_at_signup <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr5_1,
  sincerity = sinc5_1,
  intelligence = intel5_1,
  fun = fun5_1,
  ambition = amb5_1,
)

data <- delete_cols(data, others_perception_of_self_at_signup_cols)

file_name = paste0("others_perception_of_self_at_signup", ".csv")
write.csv(others_perception_of_self_at_signup, file_name, row.names = FALSE)

```


## Halfway through event (met half of scheduled dates)

### What do you look for in the opposite sex?

Please rate the importance of the following attributes in a potential date on a scale of 1-10: (1=not at all important, 10=extremely important).

```{r}

look_for_in_opp_sex_halfway_thru_event_cols <- c("attr1_s", "sinc1_s", "intel1_s", "fun1_s", "amb1_s", "shar1_s")

distinct_cols <- c(c("iid", "is_male"), look_for_in_opp_sex_halfway_thru_event_cols)

look_for_in_opp_sex_halfway_thru_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr1_s,
  sincerity = sinc1_s,
  intelligence = intel1_s,
  fun = fun1_s,
  ambition = amb1_s,
  shared_interests = shar1_s,
)

data <- delete_cols(data, look_for_in_opp_sex_halfway_thru_event_cols)

file_name = paste0("look_for_in_opp_sex_halfway_thru_event", ".csv")
write.csv(look_for_in_opp_sex_halfway_thru_event, file_name, row.names = FALSE)

```



### What do you think about yourself? (Opinion of own attributes)

Please rate your opinion of your own attributes, on a scale of 1-10 (1=awful, 10=great) -- Be honest!

```{r}

self_perception_halfway_thru_event_cols <- c("attr3_s", "sinc3_s", "intel3_s", "fun3_s", "amb3_s")

distinct_cols <- c(c("iid", "is_male"), self_perception_halfway_thru_event_cols)

self_perception_halfway_thru_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr3_s,
  sincerity = sinc3_s,
  intelligence = intel3_s,
  fun = fun3_s,
  ambition = amb3_s,
)

data <- delete_cols(data, self_perception_halfway_thru_event_cols)

file_name = paste0("self_perception_halfway_thru_event", ".csv")
write.csv(self_perception_halfway_thru_event, file_name, row.names = FALSE)

```


## Results of dates!!

```{r}

dates_results_cols = c("dec", "attr", "sinc", "intel", "fun", "amb", "shar", "like", "prob", "met", "match_es")

distinct_cols <- c(c("iid", "partner_id", "match", "is_male"), dates_results_cols)

dates_results <- data %>% get_unique_cols(distinct_cols) %>% rename(
  would_meet_partner_again = dec,
  partner_attractiveness = attr,
  partner_sincerity = sinc,
  partner_intelligence = intel,
  partner_fun = fun,
  partner_ambition = amb,
  partner_shared_interests = shar,
  liking_towards_partner = like,
  how_probable_partner_will_say_yes = prob,
  has_met_partner_before = met,
  estimated_num_matches = match_es
) %>% mutate (
  would_meet_partner_again = as.logical(would_meet_partner_again),
  has_met_partner_before = has_met_partner_before == 1
)

data <- delete_cols(data, dates_results_cols)

file_name = paste0("dates_results", ".csv")
write.csv(dates_results, file_name, row.names = FALSE)

```


## A day after event

Opinion of event

```{r}

cols <- c("satis_2", "length", "numdat_2")

distinct_cols <- c(c("iid", "is_male"), cols)

opinion_on_day_aft_event <- (data %>% get_unique_cols(distinct_cols) 
  %>% mutate(
    satisfaction_of_matches = satis_2,
    four_minutes_length_too_little = length == 1,
    four_minutes_length_too_much = length == 2,
    four_minutes_length_just_right = length == 3,
    num_speed_dates_too_few = numdat_2 == 1,
    num_speed_dates_too_many = numdat_2 == 2,
    num_speed_dates_just_right = numdat_2 == 3,
  ) 
  %>% delete_cols(cols))


data <- delete_cols(data, cols)

file_name = paste0("opinion_on_day_aft_event", ".csv")
write.csv(opinion_on_day_aft_event, file_name, row.names = FALSE)

```


### Value of attributes in decision making when evaluating dates

Now, think back to your yes/no decisions during the Speed Dating event.  Try to distribute the 100 points among these six attributes in the way that best reflects the actual importance of these attributes in your decisions. Give more points to those attributes that were more important in your decisions, and fewer points to those attributes that were less important in your decisions.  Total points must equal 100. 

```{r}

val_of_attributes_day_after_event_cols <- c("attr7_2", "sinc7_2", "intel7_2", "fun7_2", "amb7_2", "shar7_2")

distinct_cols <- c(c("iid", "is_male"), val_of_attributes_day_after_event_cols)

val_of_attributes_in_decision_making_day_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr7_2,
  sincerity = sinc7_2,
  intelligence = intel7_2,
  fun = fun7_2,
  ambition = amb7_2,
  shared_interests = shar7_2,
)

data <- delete_cols(data, val_of_attributes_day_after_event_cols)

file_name = paste0("val_of_attributes_in_decision_making_day_after_event", ".csv")
write.csv(val_of_attributes_in_decision_making_day_after_event, file_name, row.names = FALSE)

```

### What do you look for in the opposite sex?

Waves 1-5 and 10-21: You have 100 points to distribute among the following attributes -- give more points to those attributes that are more important in a potential date, and fewer points to those attributes that are less important in a potential date.  Total points must equal 100.

Waves 6-9: Please rate the importance of the following attributes in a potential date on a scale of 1-10 (1=not at all important, 10=extremely important): 

```{r}

look_for_in_opp_sex_day_after_event_cols <- c("attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2", "shar1_2")

distinct_cols <- c(c("iid", "wave", "is_male"), look_for_in_opp_sex_day_after_event_cols)

look_for_in_opp_sex_day_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr1_2,
  sincerity = sinc1_2,
  intelligence = intel1_2,
  fun = fun1_2,
  ambition = amb1_2,
  shared_interests = shar1_2,
)

data <- delete_cols(data, look_for_in_opp_sex_day_after_event_cols)

file_name = paste0("look_for_in_opp_sex_day_after_event", ".csv")
write.csv(look_for_in_opp_sex_day_after_event, file_name, row.names = FALSE)
```


### What do you think others (of your gender) look for in the opposite sex?

You have 100 points to distribute among the following attributes -- give more points to those attributes that you think your fellow men/women find more important in a potential date, and fewer points to those attributes that they find less important in a potential date.

```{r}

others_look_for_in_opp_sex_day_after_event_cols <- c("attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2", "shar4_2")

distinct_cols <- c(c("iid", "is_male"), others_look_for_in_opp_sex_day_after_event_cols)

others_look_for_in_opp_sex_day_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr4_2,
  sincerity = sinc4_2,
  intelligence = intel4_2,
  fun = fun4_2,
  ambition = amb4_2,
  shared_interests = shar4_2,
)

data <- delete_cols(data, others_look_for_in_opp_sex_day_after_event_cols)

file_name = paste0("others_look_for_in_opp_sex_day_after_event", ".csv")
write.csv(others_look_for_in_opp_sex_day_after_event, file_name, row.names = FALSE)

```


### What do you think the opposite sex looks for in a date?

Please distribute 100 points among the following attributes -- give more points to those attributes that you think are more important to members of the opposite sex when they are deciding whether to date someone.  Total points must equal 100.

```{r}

opp_sex_looks_for_in_date_day_after_event_cols <- c("attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2", "shar2_2")

distinct_cols <- c(c("iid", "is_male"), opp_sex_looks_for_in_date_day_after_event_cols)

opp_sex_looks_for_in_date_day_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr2_2,
  sincerity = sinc2_2,
  intelligence = intel2_2,
  fun = fun2_2,
  ambition = amb2_2,
  shared_interests = shar2_2,
)

data <- delete_cols(data, opp_sex_looks_for_in_date_day_after_event_cols)

file_name = paste0("opp_sex_looks_for_in_date_day_after_event", ".csv")
write.csv(opp_sex_looks_for_in_date_day_after_event, file_name, row.names = FALSE)

```


### Opinion of own attributes?

Please rate your opinion of your own attributes, on a scale of 1-10 (be honest!):

Attractiveness, Sincerity, Intelligence, Fun, Ambitions, Shared Interests

```{r}

self_perception_day_after_event_cols <- c("attr3_2", "sinc3_2", "intel3_2", "fun3_2", "amb3_2")

distinct_cols <- c(c("iid", "is_male"), self_perception_day_after_event_cols)

self_perception_day_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr3_2,
  sincerity = sinc3_2,
  intelligence = intel3_2,
  fun = fun3_2,
  ambition = amb3_2,
)

data <- delete_cols(data, self_perception_day_after_event_cols)

file_name = paste0("self_perception_day_after_event", ".csv")
write.csv(self_perception_day_after_event, file_name, row.names = FALSE)

```


### How do you think others perceive you?

Please rate yourself how you think others would rate you on each of the following attributes, on a scale of 1-10 (1=awful, 10=great):

Attractiveness, Sincerity, Intelligence, Fun, Ambitions, Shared Interests


```{r}

others_perception_of_self_day_after_event_cols <- c("attr5_2", "sinc5_2", "intel5_2", "fun5_2", "amb5_2")

distinct_cols <- c(c("iid", "is_male"), others_perception_of_self_day_after_event_cols)

others_perception_of_self_day_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr5_2,
  sincerity = sinc5_2,
  intelligence = intel5_2,
  fun = fun5_2,
  ambition = amb5_2,
)

data <- delete_cols(data, others_perception_of_self_day_after_event_cols)

file_name = paste0("others_perception_of_self_day_after_event", ".csv")
write.csv(others_perception_of_self_day_after_event, file_name, row.names = FALSE)

```



## 3-4 weeks after event


### Results

```{r}

cols <- c("you_call", "them_cal", "date_3", "numdat_3", "num_in_3")

distinct_cols <- c(c("iid", "is_male"), cols)

three_weeks_results <- (data %>% get_unique_cols(distinct_cols)
  %>% rename(
    how_many_you_contacted = you_call,
    how_many_contacted_you = them_cal,
    has_been_on_date_with_matches = date_3,
    num_matches_gone_out_with = numdat_3,
    how_many_dates = num_in_3
  )
  %>% mutate(
    has_been_on_date_with_matches = has_been_on_date_with_matches == 1
  ) 
)


data <- delete_cols(data, cols)

file_name = paste0("three_weeks_results", ".csv")
write.csv(three_weeks_results, file_name, row.names = FALSE)

```



### What do you look for in the opposite sex?

Please distribute 100 points among the following attributes -- give more to attributes that were more important in your decisions when Hurrydating, and less to attributes that were less important.  Total points must equal 100.


```{r}

look_for_in_opp_sex_weeks_after_event_cols <- c("attr1_3", "sinc1_3", "intel1_3", "fun1_3", "amb1_3", "shar1_3")

distinct_cols <- c(c("iid", "is_male"), look_for_in_opp_sex_weeks_after_event_cols)

look_for_in_opp_sex_weeks_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr1_3,
  sincerity = sinc1_3,
  intelligence = intel1_3,
  fun = fun1_3,
  ambition = amb1_3,
  shared_interests = shar1_3,
)

data <- delete_cols(data, look_for_in_opp_sex_weeks_after_event_cols)

file_name = paste0("look_for_in_opp_sex_weeks_after_event", ".csv")
write.csv(look_for_in_opp_sex_weeks_after_event, file_name, row.names = FALSE)

```


### Value of attributes in decision making when evaluating dates

Now, think back to your yes/no decisions during the night of the Speed Dating event.  Try to distribute the 100 points among these six attributes in the way that best reflects the actual importance of these attributes in your decisions. Give more points to those attributes that were more important in your decisions, and fewer points to those attributes that less less important in your decisions.  Total points must equal 100. 

```{r}

val_of_attributes_weeks_after_event_cols <- c("attr7_3", "sinc7_3", "intel7_3", "fun7_3", "amb7_3", "shar7_3")

distinct_cols <- c(c("iid", "is_male"), val_of_attributes_weeks_after_event_cols)

val_of_attributes_in_decision_making_weeks_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr7_3,
  sincerity = sinc7_3,
  intelligence = intel7_3,
  fun = fun7_3,
  ambition = amb7_3,
  shared_interests = shar7_3,
)

data <- delete_cols(data, val_of_attributes_weeks_after_event_cols)

file_name = paste0("val_of_attributes_in_decision_making_weeks_after_event", ".csv")
write.csv(val_of_attributes_in_decision_making_weeks_after_event, file_name, row.names = FALSE)

```


### What do you think others (of your gender) look for in the opposite sex?

Please rate the importance of the following attributes on a scale of 1-10 (1=not at all important, 10=extremely important):

```{r}

others_look_for_in_opp_sex_weeks_after_event_cols <- c("attr4_3", "sinc4_3", "intel4_3", "fun4_3", "amb4_3", "shar4_3")

distinct_cols <- c(c("iid", "is_male"), others_look_for_in_opp_sex_weeks_after_event_cols)

others_look_for_in_opp_sex_weeks_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr4_3,
  sincerity = sinc4_3,
  intelligence = intel4_3,
  fun = fun4_3,
  ambition = amb4_3,
  shared_interests = shar4_3,
)

data <- delete_cols(data, others_look_for_in_opp_sex_weeks_after_event_cols)

file_name = paste0("others_look_for_in_opp_sex_weeks_after_event", ".csv")
write.csv(others_look_for_in_opp_sex_weeks_after_event, file_name, row.names = FALSE)

```


### What do you think the opposite sex looks for in a date?

Please rate the importance of the following attributes on a scale of 1-10 (1=not at all important, 10=extremely important):

```{r}

opp_sex_looks_for_in_date_weeks_after_event_cols <- c("attr2_3", "sinc2_3", "intel2_3", "fun2_3", "amb2_3", "shar2_3")

distinct_cols <- c(c("iid", "is_male"), opp_sex_looks_for_in_date_weeks_after_event_cols)

opp_sex_looks_for_in_date_weeks_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr2_3,
  sincerity = sinc2_3,
  intelligence = intel2_3,
  fun = fun2_3,
  ambition = amb2_3,
  shared_interests = shar2_3,
)

data <- delete_cols(data, opp_sex_looks_for_in_date_weeks_after_event_cols)

file_name = paste0("opp_sex_looks_for_in_date_weeks_after_event", ".csv")
write.csv(opp_sex_looks_for_in_date_weeks_after_event, file_name, row.names = FALSE)

```


### Opinion of own attributes?

Please rate your opinion of your own attributes, on a scale of 1-10 (1= awful and 10=great).  Be honest!

Attractiveness, Sincerity, Intelligence, Fun, Ambitions, Shared Interests

```{r}

self_perception_weeks_after_event_cols <- c("attr3_3", "sinc3_3", "intel3_3", "fun3_3", "amb3_3")

distinct_cols <- c(c("iid", "is_male"), self_perception_weeks_after_event_cols)

self_perception_weeks_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr3_3,
  sincerity = sinc3_3,
  intelligence = intel3_3,
  fun = fun3_3,
  ambition = amb3_3,
)

data <- delete_cols(data, self_perception_weeks_after_event_cols)

file_name = paste0("self_perception_weeks_after_event", ".csv")
write.csv(self_perception_weeks_after_event, file_name, row.names = FALSE)

```


### How do you think others perceive you?

Please rate yourself how you think others would rate you on each of the following attributes, on a scale of 1-10 (1=awful, 10=great)  

Attractiveness, Sincerity, Intelligence, Fun, Ambitions, Shared Interests


```{r}

others_perception_of_self_week_after_event_cols <- c("attr5_3", "sinc5_3", "intel5_3", "fun5_3", "amb5_3")

distinct_cols <- c(c("iid", "is_male"), others_perception_of_self_week_after_event_cols)

others_perception_of_self_weeks_after_event <- data %>% get_unique_cols(distinct_cols) %>% rename(
  attractiveness = attr5_3,
  sincerity = sinc5_3,
  intelligence = intel5_3,
  fun = fun5_3,
  ambition = amb5_3,
)

data <- delete_cols(data, others_perception_of_self_week_after_event_cols)

file_name = paste0("others_perception_of_self_weeks_after_event", ".csv")
write.csv(others_perception_of_self_weeks_after_event, file_name, row.names = FALSE)

```


```{r}

file_name = paste0("matches_general", ".csv")
write.csv(data, file_name, row.names = FALSE)


```



